Diversity dynamics in Nymphalidae butterflies: Effect of phylogenetic uncertainty on diversification rate shift estimates

### 2014-10-29 MS_revised.tex
supp mat

\section*{Supporting Information Legends}
\begin{description}
 \item {\bf Supporting\_Information\_S01.nex.} MCC Nymphalidae tree from
{[}13{]}
\item {\bf Supporting\_Information\_S02.R} R script to run MEDUSA on the
MCC Nymphalidae tree from {[}13{]}. This script removes the outgroup
taxa and loads the richness data for the tree terminals.
\end{description}

\texttt{Supporting\_Information\_S03.csv}: Species richness for lineages
in Nymphalidae.

\texttt{Supporting\_Information\_S04.txt}: Results of running MEDUSA on
the MCC tree.

\texttt{Supporting\_Information\_S05\_1000\_random\_trees\_no\_outgroups.zip}:
1000 random trees from {[}13{]}.

\texttt{Supporting\_Information\_S06.R}: R script to run a MultiMEDUSA
analysis on 1000 random trees from {[}13{]}.

\texttt{Supporting\_Information\_S07\_multimedusa\_on\_1000\_trees.zip}:
Raw results from the MultiMEDUSA run on the random sample of trees from
the posterior distribution.

\texttt{Supporting\_Information\_S08.pdf}: Summary of the MulitMEDUSA
analysis on the 1000 trees from the posterior distribution.

\texttt{Supporting\_Information\_S09.tree}: MCC tree from the 1000
random trees selected from the posterior distribution.

\texttt{Supporting\_Information\_S10.R}: R script to run a MEDUSA
analysis on the MCC tree from the 1000 random trees selected from the
posterior distribution.

\texttt{Supporting\_Information\_S11.txt}: Summary results from a MEDUSA
run on the MCC tree from the 1000 random trees selected from the
posterior distribution.

\texttt{Supporting\_Information\_S12.pdf}: Figure for MEDUSA run on MCC
tree from random 1000 trees.

\texttt{Supporting\_Information\_S13.txt}: Summary results from a
MultiMEDUSA run on the 1000 random trees selected from the posterior
distribution.

\texttt{Supporting\_Information\_S14.pdf}: Probability of nodes with
estimated rates from a MultiMEDUSA run on the 1000 random trees selected
from the posterior distribution.

\texttt{Supporting\_Information\_S15.csv}: Hostplants of Nymphalidae
butterflies recorded from the literature.

\texttt{Supporting\_Information\_S16.csv}: References for hostplants
data.

\texttt{Supporting\_Information\_S17.csv}: Data matrix with character
states for hosplant use.

\texttt{Supporting\_Information\_S18.R}: R script for running the BiSSE
analysis.

\texttt{Supporting\_Information\_S19.csv}: Raw results for the BiSSE
analysis.

\texttt{Supporting\_Information\_S20.csv}: Raw results for the combined
BiSSE analysis.

\texttt{Figure S1.} Boxplot of speciation ($\lambda$) and extinction
(\(\mu\)) values for the 95\% credibility intervals of values estimated
by BiSSE analysis of diversification due to feeding on Solanaceae
plants.

\texttt{Figure S2.} BiSSE analysis of diversification of nymphalids due
to feeding on Solanaceae hostplants assuming \emph{Vanessa} and
\emph{Hypanartia} as non-Solanaceae feeders. The same pattern is
recovered, speciation and net diversification rates are significantly
higher for Solanaceae feeders ($\lambda1$), r1).

\texttt{Figure S3.} Net diversification rates of nymphalids feeding on
Solanaceae plants as estimated by combining post-burnin runs of BiSSE on
the 1000 trees from the posterior distribution.

\texttt{Figure S4.} Boxplot of speciation and extinction values for the
95\% credibility intervals of values estimated by BiSSE analysis of
diversification due to feeding on Solanaceae plants on the combined
post-burnin runs on 1000 trees from the posterior distribution.

\texttt{Figure S5.} BiSSE analysis of diversification of nymphalids due
to feeding on Apocynaceae hostplants. Speciation and net diversification
rates are similar.

>>>>

\section*{Supporting Information Legends}
\begin{description}
 \item {\bf Supporting\_Information\_S01.nex.} MCC Nymphalidae tree from
{[}13{]}

 \item {\bf Supporting\_Information\_S02.R} R script to run MEDUSA on the
MCC Nymphalidae tree from {[}13{]}. This script removes the outgroup
taxa and loads the richness data for the tree terminals.

 \item {\bf Supporting\_Information\_S03.csv} Species richness for lineages
in Nymphalidae.

 \item {\bf Supporting\_Information\_S04.txt} Results of running MEDUSA on
the MCC tree.

 \item {\bf Supporting\_Information\_S05\_1000\_random\_trees\_no\_outgroups.zip} 1000 random trees from {[}13{]}.

 \item {\bf Supporting\_Information\_S06.R} R script to run a MultiMEDUSA
analysis on 1000 random trees from {[}13{]}.

 \item {\bf Supporting\_Information\_S07\_multimedusa\_on\_1000\_trees.zip} Raw results from the MultiMEDUSA run on the random sample of trees from
the posterior distribution.

 \item {\bf Supporting\_Information\_S08.pdf} Summary of the MulitMEDUSA
analysis on the 1000 trees from the posterior distribution.

 \item {\bf Supporting\_Information\_S09.tree} MCC tree from the 1000
random trees selected from the posterior distribution.

 \item {\bf Supporting\_Information\_S10.R} R script to run a MEDUSA
analysis on the MCC tree from the 1000 random trees selected from the
posterior distribution.

 \item {\bf Supporting\_Information\_S11.txt} Summary results from a MEDUSA
run on the MCC tree from the 1000 random trees selected from the
posterior distribution.

 \item {\bf Supporting\_Information\_S12.pdf} Figure for MEDUSA run on MCC
tree from random 1000 trees.

 \item {\bf Supporting\_Information\_S13.txt} Summary results from a
MultiMEDUSA run on the 1000 random trees selected from the posterior
distribution.

 \item {\bf Supporting\_Information\_S14.pdf} Probability of nodes with
estimated rates from a MultiMEDUSA run on the 1000 random trees selected
from the posterior distribution.

 \item {\bf Supporting\_Information\_S15.csv} Hostplants of Nymphalidae
butterflies recorded from the literature.

 \item {\bf Supporting\_Information\_S16.csv} References for hostplants
data.

 \item {\bf Supporting\_Information\_S17.csv} Data matrix with character
states for hosplant use.

 \item {\bf Supporting\_Information\_S18.R} R script for running the BiSSE
analysis.

 \item {\bf Supporting\_Information\_S19.csv} Raw results for the BiSSE
analysis.

 \item {\bf Supporting\_Information\_S20.csv} Raw results for the combined
BiSSE analysis.

 \item {\bf Figure S1.} Boxplot of speciation ($\lambda$) and extinction
($\mu$) values for the 95\% credibility intervals of values estimated
by BiSSE analysis of diversification due to feeding on Solanaceae
plants.

 \item {\bf Figure S2.} BiSSE analysis of diversification of nymphalids due
to feeding on Solanaceae hostplants assuming \emph{Vanessa} and
\emph{Hypanartia} as non-Solanaceae feeders. The same pattern is
recovered, speciation and net diversification rates are significantly
higher for Solanaceae feeders $\lambda1$, r1).

 \item {\bf Figure S3.} Net diversification rates of nymphalids feeding on
Solanaceae plants as estimated by combining post-burnin runs of BiSSE on
the 1000 trees from the posterior distribution.

 \item {\bf Figure S4.} Boxplot of speciation and extinction values for the
95\% credibility intervals of values estimated by BiSSE analysis of
diversification due to feeding on Solanaceae plants on the combined
post-burnin runs on 1000 trees from the posterior distribution.

 \item {\bf Figure S5.} BiSSE analysis of diversification of nymphalids due
to feeding on Apocynaceae hostplants. Speciation and net diversification
rates are similar.
\end{description}
